Stability and Chaos in Multi-agent Reinforcement Learning

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

An important result in modelling such multi-agent systems \fb{check
  consistency of multi agent $\to$ multi-agent.} from the EGT
perspective is that, when games are learnt and the assumptions of
rationality and perfect information are lifted, games may not converge
to an equilibrium. Instead, as shown in \cite{Sanders2018}, the
dynamics may be more complex, and even chaotic (see
Section~\ref{sec::DynamicalBehaviours}). The present work further
describes that the emergence of such behaviours depends on the
parameters of the games and the learning algorithm. For the analysis
of multi-agent systems whose behaviour is inter-dependent, it is
desirable that the system be such that the game convergence to a
stable equilibrium. Without this, it is inherently impossible to
predict the outcome of learning.

\paragraph{Contribution}
In this study, we will be considering the question: under what choice of parameters is a
multi-agent system, which is trained on an iterated game using Q-Learning, likely to converge to an
equilibrium as opposed to displaying complex, or unstable behaviours? In investigating this question, we will make the
following assumptions:

\begin{enumerate}
    \item There are a finite set of agent, though the size $p$ of the set is arbitrary. 
    \item The agents have a large, but discrete, strategy space: during the theoretical study, we
    will make the assumption that the number of actions $N$ goes to infinity.
    \item The agents are homogeneous. This requires that all agents have the same parameters and are
    trained using the same algorithm. Since this is typically the case in reinforcement learning
    studies, it is not an unreasonable assumption, but does present an interesting avenue for future
    work.
    \item The agents are trained on stateless, normal form games (i.e. the environment is static).
\end{enumerate}

@@

In this section we present an overview of the vast literature which considers the study of Reinforcement Learning (RL) from an evolutionary game dynamics perspective, as well as touching upon some important results and research within the field of game dynamics.

>>>>

An important result in modelling such multi-agent systems \fb{check
  consistency of multi agent $\to$ multi-agent.} from the EGT
perspective is that, when games are learnt and the assumptions of
rationality and perfect information are lifted, games may not converge
to an equilibrium. Instead, as shown in \cite{Sanders2018}, the
dynamics may be more complex, and even chaotic (see
Sec.~\ref{sec::DynamicalBehaviours}) \fb{Section $\to$ Sec.}. The present work further
describes that the emergence of such behaviours depends on the
parameters of the games and the learning algorithm. For the analysis
of multi-agent systems whose behaviour is inter-dependent, it is
desirable that the system be such that the game convergence to a
stable equilibrium. Without this, it is inherently impossible to
predict the outcome of learning.

\paragraph{Contribution}
In this study, we will be considering the question: under what choice
of parameters is a multi-agent system, which is trained on an iterated \fb{normal-form}
game using Q-Learning, likely to converge to an equilibrium as opposed
to displaying complex, or unstable behaviours? In investigating this
question, we will make the following assumptions:

\begin{enumerate}
    \item There is a finite set of agent, though its size $p$ can be
      arbitrarily large.

    \item The agents have a large, but discrete, strategy space:
      during the theoretical study, we will make the assumption that
      the number $N$ of actions goes to infinity.

  \item The agents are homogeneous. This requires that all agents have
    the same parameters and are trained using the same
    algorithm. Since this is typically the case in reinforcement
    learning studies, it is not an unreasonable assumption, but does
    present an interesting avenue for future work.

  \item The agents are trained on stateless, normal form games
    (i.e., the environment is static).
\end{enumerate}

\fb{I would summarize here the main findings of the paper in 10-15 lines.}

@@

In this section we present an overview of the vast literature which
considers the study of reinforcement learning from an evolutionary
game dynamics perspective, as well as touching upon some important
results and research within the field of game dynamics.
